### 2012-06-13 inst/examples/Sethi_policyfns.Rmd
Sethi Policy functions results

Clear the workspace and load package dependencies: 
``` {r  setup, echo=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

Plot the policy function:

``` {r policyfn_plot}
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

and the value function:

``` {r valuefn_plot}
qplot(x_grid, opt$V, xlab="stock size", ylab="value")
````

@@

``` {r  parallel2}
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
```

Plot the policy function:

``` {r policyfn_plot2}
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

and the value function:

``` {r valuefn_plot2}
qplot(x_grid, opt$V, xlab="stock size", ylab="value")
````

>>>>

Clear the workspace and load package dependencies: 
``` {r  setup, echo=FALSE, cache=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
```

``` {r sdp1}
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

@@

``` {r  find_dp_opt }
measure <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

@@

``` {r  parallel2}
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
growth <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
```

### Large implementation error

``` {r  noise_dists3}
sigma_g <- 0.01    # Noise in population growth
sigma_m <- 0.01     # noise in stock assessment measurement
sigma_i <- 0.25     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

``` {r  parallel3}
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
imp <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
```

``` {r plots}
require(reshape2)
policy <- melt( data.frame(stock=x_grid, implementation = x_grid[imp$D[,1]], measurement = x_grid[measure$D[,1]], growth = x_grid[growth$D[,1]]), id="stock")
value <-  melt(data.frame(stock=x_grid, implementation = imp$V, measurement = measure$V, growth = growth$V), id="stock")
ggplot(policy) + geom_point(aes(stock, stock-value, color=variable))
ggplot(value) + geom_point(aes(stock, stock-value, color=variable))
ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))
ggplot(value) + geom_smooth(aes(stock, stock-value, color=variable))
````
